Identifying Inter-Genomic Repeats Using Fast, Approximate Methods for Betweenness Centrality

### 2015-05-07 manuscript/manuscript.tex
minor bug fixed
Added example repeat graph
Added captions/table cutoff result.

@@

Another cutoff criteria we test is based on \textit{interquartile range(IQR)}. Let $Q_{1}$,$Q_{2}$, and $Q_{3}$ denote lower, midle and upper quartile respectiely. IQR can be defined as the difference between the upper and lower quartile. So, $IQR = Q_{3} - Q_{1}$. For the values of centrality, we calculate upper quartile, middle quartile, lower quartile and IQR. For filtering, we mark all the nodes with centrality more than $Q_{2} + 1.5*IQR$ as repeats. The advantage of this method is that it does not make any assumptions about the distribution of underlying data.

@@

>>>>

\begin{figure*}[htbp]
\centering
\includegraphics[width=\textwidth]{es_mix_200kb_k21.png}
\caption{Assembly graph of a simulated community consisting of 200 Kbp subsets of \textit{Escherichia coli} str. K-12 MG1655 and emph{Staphylococcus aureus}.  Nodes are colored and sized based on their relative betweenness centrality. The highlighted nodes are inter-genomic repeats whose deletion would separate the graph.}
\label{fig:sampled_nodes}
\end{figure*}

@@

Another cutoff criteria we test is based on \textit{interquartile range(IQR)}. Let $Q_{1}$,$Q_{2}$, and $Q_{3}$ denote lower, middle and upper quartile respectiely. IQR can be defined as the difference between the upper and lower quartile. So, $IQR = Q_{3} - Q_{1}$. For the values of centrality, we calculate upper quartile, middle quartile, lower quartile and IQR. For filtering, we mark all the nodes with centrality more than $Q_{2} + 1.5*IQR$ as repeats. The advantage of this method is that it does not make any assumptions about the distribution of underlying data.

@@

\begin{table}[h]
\centering
\caption[]{Statistical measures of performance using different cutoff levels for marking a node as an inter-genomic repeat on the simulated 10 genome assembly graph.  $c=3$ is Bambus2's default cutoff level and \textsc{irq} utilizes the different quartile values. }
\begin{tabular}{lllll}
 & $c=3$        & \textsc{irq}   \\
\hline
sensitivity & 0.0584 & 0.344 \\
specificity & 0.993  & 0.909 \\
precision   & 0.250  & 0.125 \\
\hline 
\end{tabular}
\end{table}
